Ricci and transit times

### 2014-12-13 prep_figures/commute/curvature-MCT.Rmd
Checking out commute time results.

---
title: "Ricci and commute time"
runtime: shiny
output: html_document
---

@@

d <- get_results("../../results-rspr/commute6.mat")
d$dist <- as.factor(d$dist)

d %>%
  ggvis(x = ~kappa, y = ~MCT) %>%
  layer_points(size = 5, fill = ~dist) %>%
  # A dummy layer so that we can use text in the tooltip.
  layer_text(text := ~info, fontSize := 0) %>%
  add_axis("x", grid = FALSE) %>%
  add_axis("y", grid = FALSE) %>%
  add_legend(c("fill"), properties=legend_props(legend=list(y=0))) %>%
  add_tooltip(function(df) df$info)
```

>>>>

---
title: "Ricci and transit times"
runtime: shiny
output: html_document
---

@@

# d <- get_results("../../results-rspr/commute-nodata/commute6.mat")
# d$dist <- as.factor(d$dist)

d5 <- get_results("../../results-rspr/commute-onesplit/123_45-1v5c.tsv")
d6 <- get_results("../../results-rspr/commute-onesplit/123_456-1v5c.tsv")
d <- d6

d %>%
  ggvis(x = ~kappa, y = ~MAT) %>%
  #ggvis(x = ~kappa, y = ~MCT) %>%
  layer_points() %>%
  # A dummy layer so that we can use text in the tooltip.
  layer_text(text := ~info, fontSize := 0) %>%
  add_axis("x", grid = FALSE) %>%
  add_axis("y", grid = FALSE) %>%
  add_tooltip(function(df) df$info)
```
